EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-18 paper/paper.tex
paper updates

\section{Conclusion and Future Work}
Code clones are very common in medium to large scale software applications.
Detecting and refactoring unnecessary clones can help us provide cleaner, easier to understand, and readily reusable code.
However, there are many different types of clones and many subtle implications while dealing with them when coupling and
inheritance is involved. Our proposed solution, EasyMerge, is a clone refactoring tool based on anti-unification clone detector 
CloneDigger, that can handle most Type-1 clones and many Type-2 clones. It fixes external variable and function reference
and provide merge recommendation based on evaluation of externality and package information analysis.

>>>>

\section{Conclusion and Future Work}
Code clones are very common in medium to large scale software applications.
Detecting and refactoring unnecessary clones can help us provide cleaner, easier to understand, and readily reusable code.
However, there are many different types of clones and many subtle implications while dealing with them when coupling and
inheritance is involved. Our proposed solution, EasyMerge, is a clone refactoring tool based on anti-unification clone detector 
CloneDigger, that can handle most Type-1 clones and many Type-2 clones. It fixes external variable and function reference
and provide merge recommendation based on evaluation of externality and package information analysis.
Moreover, EasyMerge guarantees the consistency of functionality before and after code merging.

However, EasyMerge still has limitations. First of all, not all code clones can be detected by CloneDigger or any existing
code clone detection approach in general. For future work, we may upgrade EasyMerge's clone detection engine to locate
more clones in code base.

Secondly,
